---
title: "Singapore hawker centers in Bukit Timah and Bukit Merah"
author: 
  - Chris Yong Hong Sen
thanks: "Code and data are available at: [https://github.com/Monoji77/hawker_center_singapore](https://github.com/Monoji77/hawker_center_singapore)."
date: today
date-format: long
format: 
  html:
    theme: darkly
  
number-sections: true
bibliography: references.bib
---

# Introduction
This paper explores hawker centers in singapore and it's relationship with housing. @citeR was used for the creation of this page. httr2 was used to obtain data via API [@httr2] which was then saved as geojson files using sf package [@sf]. The sf package was then used to parse in spatial data from the saved geojson files. Tidyverse was used to manipulate data from geometry files [@tidyverse] and tmap package was used to generate and customise the desired maps [@tmap]. 

The dataset was obtained from @onemap_api.

The rest of the paper includes the density map of either landed properties or 1 to 3 room hdb housing, layered with hawker centers. This allows us to geo-visualise the relationship between housing and hawker centers.
```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(sf)
library(tmap)
library(httr)
```



```{r}
#| include: FALSE
#| warning: false
#| message: false

tmap_mode('view')
#tmap_mode('plot')
hawker_geometry <-st_read("../data/02-analysis_data/hawker_geometry.geojson") |>
  select(Name, geometry) #|>
  #filter(Name %in% c('BUKIT TIMAH', 'BUKIT MERAH'))
hawker_geometry_clean <- cbind(col1 = 'Hawker', hawker_geometry)
hawker_map <- 
  #mutate(Name = pln_area_name) |>
  tm_shape(hawker_geometry_clean) + 
  tm_symbols(col = 'palegreen3',
             size = 0.3,
             alpha = 0.7,
             popup.vars = c('Hawker Region: ' = 'Name'))#col = 'Name',
             #legend.col.show = FALSE)

housing_geometry <- st_read("../data/02-analysis_data/housing_geometry.geojson") #|>
  #filter(pln_area_n  %in% c('BUKIT TIMAH', 'BUKIT MERAH'))

# condo_landed <- tm_shape(housing_geometry) + 
#   tm_polygons(col='condo_landed',
#               palette = 'Blues') +
#   hawker_map
# condo_landed
```

# Region coloured on number of landed properties {#sec-landed}
```{r}
#| echo: FALSE
#| warning: false
#| message: false
landed <- tm_shape(housing_geometry) + 
  tm_polygons(col='landed',
              palette = 'Blues') +#,
              #alpha=0.6,
              #lwd=2) +
  hawker_map +
  tm_layout(main.title = "Region coloured on number of landed properties") +
  tm_basemap("OpenStreetMap")
landed
```


# Region coloured by cheaper housing {#sec-cheap}
```{r}
#| echo: FALSE
#| warning: false
#| message: false
#| fig-subcap: Data was obtained from [OneMap]()


hdb_one_to_three_rooms <- tm_shape(housing_geometry) + 
  tm_polygons(col='hdb_one_to_three_rooms',
              alpha = 0.8) +
  hawker_map +
  tm_basemap("Esri.WorldTopoMap")

hdb_one_to_three_rooms

# save maps
#tmap_save(landed, '../other/maps/landed_hawker_map.html')
#tmap_save(hdb_one_to_three_rooms, '../other/maps/hdb_hawker_map.html')
```


\newpage


# References


